Humanized Quadcopter Swarm System for IARC 2019

### 2019-06-01 IARC_Paper_2019/Paper.tex
Small changes

\title{Intelligent Quadcopter for IARC 2019}

@@

\section*{INTRODUCTION}
	Previous aerial robotics missions have always allowed for GPS or other external active position estimation  that allowed for constant locational awareness. Location data is important to any mission, as proper state awareness prevents various failures, including complete loss of control for the drone. Thus, Mission 8 requires novel solutions to deriving this critical state data as GPS is forbidden. Additionally, the aircrafts must be capable of taking commands in a humanized "natural" fashion and avoid other aircrafts without being informed of those other aircrafts' locations.

	Texas Aerial Robotics addresses these challenges by utilizing computer vision. TAR uses ORBSLAM2, an "Open-Source SLAM System for Monocular, Stereo and RGB-D Cameras" to create maps of the arena in real time. The drone creates pointclouds of the objects in view using the stereo camera and combines sections together to create the maps. This means that should a section of the map start showing drift, the ORBSLAM2/ORBSLAMM System will toss out just the section while maintaining as much of the map as possible. TAR hopes to combine the processing between the multiple drones to have them work together on one map. These drones also solve for the QR code that is the combination the human needs for collecting the objects. TAR implements the "humanized" control aspect of the system through voice control using an Android app that connects to all of the air vehicles. The drones are also built with safety features for a plethora of other objects that may be on the field through its man-safe propellers for any humans and sonar sensors for avoiding other air vehicles at all times.

@@

The eCalc online tool was used to validate our calculations, and as seen by the generated graph below, there should be no issue reaching above 8 minute flight times at speeds below 15 [mph].

%		\begin{figure}[!htbp]
%			\begin{center}
%				\includegraphics[width=0.75\textwidth]{powerGraph}
%			\end{center}
%		\end{figure}

>>>>

\title{Humanized Quadcopter Swarm System for IARC 2019}

@@

\section*{INTRODUCTION}
	Previous aerial robotics missions have always allowed for GPS or other external active position estimation  that allowed for constant locational awareness. Location data is important to any mission, as proper state awareness prevents various failures, including complete loss of control for the drone. Thus, Mission 8 requires novel solutions to deriving this critical state data as GPS is forbidden. Additionally, the aircrafts must be capable of taking commands in a humanized ``natural'' fashion and avoid other aircrafts without being informed of those other aircrafts' locations.

	Texas Aerial Robotics addresses these challenges by utilizing computer vision. TAR uses ORBSLAM2, an ``Open-Source SLAM System for Monocular, Stereo and RGB-D Cameras'' to create maps of the arena in real time. The drone creates pointclouds of the objects in view using the stereo camera and combines sections together to create the maps. This means that should a section of the map start showing drift, the ORBSLAM2/ORBSLAMM System will toss out just the section while maintaining as much of the map as possible. TAR hopes to combine the processing between the multiple drones to have them work together on one map. These drones also solve for the QR code that is the combination the human needs for collecting the objects. TAR implements the ``humanized'' control aspect of the system through voice control using an Android app that connects to all of the air vehicles. The drones are also built with safety features for a plethora of other objects that may be on the field through its man-safe propellers for any humans and sonar sensors for avoiding other air vehicles at all times.

@@

The eCalc online tool was used to validate our calculations, and as seen by the generated graph, there should be no issue reaching 8+ minute flight times at speeds below 15 [mph].

		\begin{figure}[!htbp]
			\begin{center}
				\includegraphics[width=0.6\textwidth]{powerGraph}
			\end{center}
		\end{figure}

\pagebreak
